### 2021-03-31 BMC-Journal of Biomedical Semantics/submission 0/bmc_template/results.tex
more code
some fixes

The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed syntactic and semantic matching process with fuzzy string matching, only semantic matching of attribute names using sentence embedding, and with multiple human annotated versions of the schema map. Using the 21,809 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element. All nodes, for which the SchemaName part of the name is same, are then marked with ``-", and these are omitted from further processing. This various versions of this dataset (D) are available at \textbf{url}.

@@

In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators. A visualization of the resultant Cohen's Kappa score for the 257 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}. The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators. The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.

>>>>

The validity of our proposed approach has been evaluated using several techniques, including comparison of the proposed syntactic and semantic matching process with fuzzy string matching, only semantic matching of attribute names using sentence embedding, and with multiple human annotated versions of the schema map. Using the 21,873 AA pairs, we created a two dimensional matrix, of AA identifiers, whereby each cell refers to a ``SchemaName\_TableName\_AttributeName" element. All nodes, for which the SchemaName part of the name is same, are then marked with ``-", and these are omitted from further processing. This various versions of this dataset (D) are available at \textbf{url}.

@@

In order to evaluate the accuracy and precision rates of these methodologies, we then compared the results of our computed methods $D_f$, $D_b$, and $D_p$, with the average scored datasets by the human annotators. A visualization of the resultant Cohen's Kappa score for the 261 participating attributes, is shown in \textbf{figComputedComparisonKappaScore}. The bar chart shown in this visualization, indicates, an overall greater positive agreement between our proposed methodolody $D_p$, and the average scores of the annotators. The same is shown by the \textbf{orange} colored peaks in this dataset, which in all cases is either equivalent to the other approaches ($D_f$ and $D_b$), or better than them.
